Spectral partitioning identifies individual heterogeneity in the functional network topography of ventral and anterior medial prefrontal

### 2019-09-14 Manuscript.Rmd
tiny hiccup error

# stats: one sample t's per hemisphere/region
curvStats <- curvCors %>% 
                group_by(region, Hemisphere) %>% 
                summarise(meanCor = mean(Correlation),
                          seCor = sd(Correlation) / sqrt(nSubj),
                          TStat = round(t.test(Correlation)$statistic, digits = 2),
                          p_unc = t.test(Correlation)$p.val,
                          Sig = p < 0.05,
                          ES = DescTools::CohenD(Correlation))

>>>>

# stats: one sample t's per hemisphere/region
curvStats <- curvCors %>% 
                group_by(region, Hemisphere) %>% 
                summarise(meanCor = mean(Correlation),
                          seCor = sd(Correlation) / sqrt(nSubj),
                          TStat = round(t.test(Correlation)$statistic, digits = 2),
                          p_unc = t.test(Correlation)$p.val,
                          #Sig = p < 0.05,
                          ES = DescTools::CohenD(Correlation))
